Wide binaries in Gaia DR1

### 2016-09-23 paper/ms.tex
add equations decribing the FML ratio

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transpose}[1]{{#1}^{\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}

@@

\title{}
\author{}

@@

\begin{abstract}
% Context
% Aims
% Methods
% Results
\end{abstract}

@@

>>>>

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\matrx}[1]{\mathbf{#1}}
\newcommand{\kms}{\rm km~s^{-1}}

@@

\title{Wide binaries in Gaia DR1}
\author{People}

@@

\begin{abstract}
Blerg.
% Context
% Aims
% Methods
% Results
\end{abstract}

@@

\section{Methods} \label{sec:methods}

We want to evaluate the likelihood ratio
\begin{equation}
  \frac{p(\propm_1, \propm_2)_{\vperp_1 = \vperp_2}}
  {p(\propm_1, \propm_2)_{\vperp_1 \neq \vperp_2}}
\end{equation}
where
\begin{multline}
  p(\propm_1, \propm_2)_{\vperp_1 = \vperp_2} =
    \int \, \dd d_1 \, \dd d_2 \, \dd \vperp \,
    p(\propm_1 \given d_1, \vperp, \matrx{C}_{\mu,1}) \,
    p(\propm_2 \given d_2, \vperp, \matrx{C}_{\mu,2}) \\
    p(d_1 \given \varpi_1, \sigma_{\varpi_1}) \,
    p(d_2 \given \varpi_2, \sigma_{\varpi_2}) \,
    p(\vperp)
\end{multline}
and
\begin{multline}
  p(\propm_1, \propm_2)_{\vperp_1 \neq \vperp_2} =
    \int \, \dd d_1 \, \dd d_2 \, \dd \vperp_1 \, \dd \vperp_2 \,
    p(\propm_1 \given d_1, \vperp_1, \matrx{C}_{\mu,1}) \,
    p(\propm_2 \given d_2, \vperp_2, \matrx{C}_{\mu,2}) \\
    p(d_1 \given \varpi_1, \sigma_{\varpi_1}) \,
    p(d_2 \given \varpi_2, \sigma_{\varpi_2}) \,
    p(\vperp_1) \, p(\vperp_2)
\end{multline}
We'll assume the sky positions $(\alpha, \delta)$ are known perfectly, and that
the uncertainties in proper motion components, $\propm=(\mu_\alpha,
\mu_\delta)$, are Gaussian with known covariance matrix $\matrx{C}_\mu$ so that
\begin{equation}
  p(\propm \given d, \vperp, \matrx{C}) = \left[\det\left(\frac{\matrx{C}_\mu^{-1}}{2\pi}\right)\right]^{1/2} \, \exp \left[ -\frac{1}{2} \transp{\left(\propm - \frac{\vperp}{d}\right)} \, \matrx{C}_\mu^{-1} \, \left(\propm - \frac{\vperp}{d}\right) \right]
\end{equation}

Our distance posterior pdfs, $p(d \given \varpi, \sigma_\varpi)$, will come from
Coryn Bailer-Jones.

Our priors on tangential velocity components, $i$, will be something like:
\begin{equation}
  p(v^\perp_i) = \mathcal{N}(0, 30) \, \kms
\end{equation}
